---
title: "Onion Assignment - Shahid Khan"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load all packages
```{r}
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
library(httr)
library(data.table)
library(stringr)
library(prophet)

```

#Aquire the daily onion data from nhrdf.org
```{r}
getwd()
setwd("C:/bigdata")
page=read_html("DailyWiseMarketArrivals_2016.html")
table_node=html_node(page,"#dnn_ctr966_DailyWiseMarketArrivals_GridView1")
table=html_table(table_node)
str(table)
df=table

```
#Start refining the data by putting in column names which are meaningful
```{r}
dim(df)
column_name = c('date','market','quantity','priceMin','priceMax','priceMod')
colnames(df)=column_name
df$priceMax=as.numeric(df$priceMax)
df$priceMin=as.numeric(df$priceMin)
df$priceMod=as.numeric(df$priceMod)
df$date = as.Date(df$date,format = "%d/%B/%Y")
str(df)

```
#Remove the NA from the dataset and mutate data
```{r}
df=filter(df,!is.na(priceMod))
df=filter(df,!is.na(priceMax))
df=filter(df,!is.na(priceMin))
df1 <- df %>% mutate(market1 = market) %>% separate(market1,c("city", "state"),sep="\\(")
unique(df1$state)
```
#Data refining for cities and states
```{r}
str(df1)
#Find out cities which are not a duplicate
citiesWithNoState = df1 %>% filter(is.na(state))
citiesWithNoState = citiesWithNoState[!duplicated(citiesWithNoState[,c("city")]),]
#put all cities with no state with either
#View(citiesWithNoState$city)
#find all states
statesWithNoDupes = df1[!duplicated(df1[,c("state")]),]
df1$state = str_replace(df1$state,"\\)","")
df1$state = str_trim(df1$state)

#find cities which have the following state codes
#F&V,KER,Others,RAJ,RJ,CHATT,CHGARH
df2=df1 %>% filter(state == c('KER','Others','RAJ','RJ','CHATT','CHGARH'))
df2=df2[!duplicated(df2[,c("state","city")]),]

sizeofdf2=nrow(df2)
#print the states identified with each of these cities
for(i in 1:sizeofdf2){
  cat(df2[i,]$city,df2[i,]$state,"\n")
}

# from the output below, we can make the city pratapgarh to be same as others in RAJ
# In addition, CHATT and CHGARG are same state i.e. chhatisgarh
df1$state=str_replace(df1$state,"CHATT","CHGARH")
df1$state=str_replace(df1$state,"RJ","RAJ")
df1$state=str_replace(df1$state,"TELANGANA","Telangana")
df1$state=str_replace(df1$state,"Others","DELHI")
df1$state=str_replace(df1$state,"F\\&V","MP")
#remove special characters like "." from states
df1$state=str_replace_all(df1$state,"\\.","")

#first find all cities which dont have a state
allCities = df1 %>% filter(is.na(state))
unique(allCities[,c('city')])

#Now start replacing all of them with appropriate state
df1$state[df1$city=='DELHI'] <- 'DELHI'
df1$state[df1$city=='BANGALORE'] <- 'KNT'
df1$state[df1$city=='BULANDSHAHR'] <- 'UP'
df1$state[df1$city=='SHAHJAHANPUR'] <- 'UP'
df1$state[df1$city=='CHENNAI'] <- 'TN'
df1$state[df1$city=='MUMBAI'] <- 'MS'
df1$state[df1$city=='NAGPUR'] <- 'MS'
df1$state[df1$city=='JAIPUR'] <- 'RAJ'
df1$state[df1$city=='HYDERABAD'] <- 'Telangana'
df1$state[df1$city=='GUWAHATI'] <- 'AS'
df1$state[df1$city=='PATNA'] <- 'BHR'
df1$state[df1$city=='IMPHAL'] <- 'Meghalaya'
df1$state[df1$city=='KOLKATA'] <- 'WB'
df1$state[df1$city=='LUCKNOW'] <- 'UP'
df1$state[df1$city=='BHOPAL'] <- 'MP'
df1$state[df1$city=='CHANDIGARH'] <- 'PB'
df1$state[df1$city=='JAMMU'] <- 'JK'
df1$state[df1$city=='Others'] <- 'Delhi'
df1$state[df1$city=="F\\&V "] <- 'MP'

#Below lines of code are just to check whether there could be other rows
#with Others as state
allFAndVState = df1 %>% filter(state == "Others")
str(df1)

```
#sum up the quantity and arrange them in desc order to find the highest consuming state
```{r}
dfQty = df1 %>% group_by(state) %>% summarize(yearQty=sum(quantity)) %>% arrange(desc(yearQty))
summary(dfQty)
#plot the usage
ggplot(data=dfQty) + aes(reorder(state,yearQty),yearQty,fill=state) + geom_col(width=1) +coord_flip()

```


#What is the percent usage from the above
```{r}
#In terms of percentage
ggplot(dfQty,aes(fill=state)) + 
         geom_bar(aes(x=state,y = (yearQty)/sum(yearQty)),geom ="text",stat = "identity") + scale_y_continuous(labels = scales::percent)

#% as a label on each state
ggplot(dfQty,aes(x=state, y=(yearQty)/sum(yearQty), fill=state)) +
  geom_bar(stat="identity") + geom_text(aes(label=paste0(sprintf("%1.1f", (yearQty)/sum(yearQty)*100),"%"), colour="white"))

```

#scatter plot for consumption in top 3 states
```{r}
ggplot(subset(df1,state %in% c("MS","KNT","GUJ")),aes(x=date,y=quantity,col=state)) + geom_point()

```

#PriceTrend in the top 3 states
```{r}
ggplot(subset(df1,state %in% c("MS","KNT","GUJ")),aes(x=date,y=priceMod,col=state)) + geom_point()
```

#Predict prices for the next 30 days in the state which consumes the most 
```{r}
dfBang = df1 %>% filter(state=="MS") %>% select(date,priceMod)
colnames(dfBang) = c('ds','y')
m=prophet(dfBang)
future = make_future_dataframe(m,period=30,freq = 'd')
forecast = predict(m,future)
plot(m,forecast)
```

#Identify some forecast trend
```{r}
str(forecast)
max(forecast$trend)
min(forecast$trend)
```

#Conclusions
1. Maharashtra is top consuming state
2. Maharashtra, Karnataka and Gujarat are the top 3 consuming states. Together they consume ~75% of the overall produce.
3. In Gujarat, there is a spike in consumption in the first half of the year, in karnataka the consumption spikes in the 4th quarter. In Maharashtra the consumption is constant throughout the year.
4. Price is similar across the top 3 states throughout

