---
title: "ShahidKhan_Aug17_SL_Asmt"
author: "Shahid Khan"
date: "4 November 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load all libraries
```{r}
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
library(httr)
library(data.table)
library(woe)
library(sqldf)

```
## R Markdown
```{r}
## Let us first import our dataset for modeling
setwd("C:/bigdata")

PL_XSELL <- read.table("PL_XSELL_201708.csv",sep = ",", header = T)

summary(PL_XSELL)
table(PL_XSELL$TARGET)
str(PL_XSELL)
#Convert some of the variables into their appropriate type
#Convert ACC_OP_DATE into date type
fmts <- c("%m-%d-%Y", "%m/%d/%Y")
PL_XSELL$ACC_OP_DATE <- as.Date(as.numeric(apply(outer(PL_XSELL$ACC_OP_DATE, fmts, as.Date), 1, na.omit)), "1970-01-01")
PL_XSELL$CUST_ID <- as.character(PL_XSELL$CUST_ID)
PL_XSELL$OCCUPATION <- as.character(PL_XSELL$OCCUPATION)
PL_XSELL$AGE_BKT <- as.character(PL_XSELL$AGE_BKT)



```

## Identify the quartiling and Draw box plots for some of the variables
```{r}
quantile(PL_XSELL$BALANCE, 
         c(0.01, 0.05, 0.1, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99, 1))

quantile(PL_XSELL$HOLDING_PERIOD, 
         c(0.01, 0.05, 0.1, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99, 1))

quantile(PL_XSELL$SCR, 
         c(0.01, 0.05, 0.1, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99, 1))

quantile(PL_XSELL$FLG_HAS_CC, 
         c(0.01, 0.05, 0.1, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99, 1))

#special technique of quartiling by date
dq <- quantile(ifelse(class(PL_XSELL$ACC_OP_DATE) != "Date", PL_XSELL$ACC_OP_DATE, as.integer(PL_XSELL$ACC_OP_DATE)), 
         c(0.01, 0.05, 0.1, 0.25, 0.50, 0.75, 0.90, 0.95, 0.99, 1))
class(dq) <- "Date"

#Boxplot for balance

boxplot(PL_XSELL$BALANCE , 
        main= "Balance box plot" ,
        xlab = "Overall Base"
)
# Do outlier treatment for balance

PL_XSELL$BAL_CAP <- 
  ifelse(PL_XSELL$BALANCE > 1500000, 1500000, PL_XSELL$BALANCE)

#Box plot for BAL_CAP
boxplot(PL_XSELL$BALANCE , 
        main= "BAL_CAP box plot" ,
        xlab = "Overall Base"
)


boxplot(PL_XSELL$HOLDING_PERIOD , 
        main= "Holding Period box plot" ,
        xlab = "Overall Base"
)

boxplot(PL_XSELL$AGE , 
        main= "Age Box Plot" ,
        xlab = "Overall Base"
)

boxplot(PL_XSELL$SCR , 
        main= "Score Box Plot" ,
        xlab = "Overall Base"
)

boxplot(PL_XSELL$FLG_HAS_CC , 
        main= "Flag has charges Box Plot" ,
        xlab = "Overall Base"
)


```

#Identify significant variables using IV
```{r}

#Converting the ACC_OP_DATE as a character variable for IV
PL_XSELL$ACC_OP_DATE <- as.character(PL_XSELL$ACC_OP_DATE)

iv.plot.summary(iv.mult(PL_XSELL[,!names(PL_XSELL) %in% c("CUST_ID")],
                        "TARGET",TRUE, verbose = TRUE))

iv <- iv.mult(PL_XSELL[,!names(PL_XSELL) %in% c("CUST_ID")],
              "TARGET",FALSE)

iv
str(PL_XSELL)
# Following is what iv produces
#SUSPICIOUS - ACC_OP_DATE
#AVERAGE - HOLDING_PERIOD, NO_OF_L_DR_TXNS,TOT_NO_OF_L_TXNS NO_OF_ATM_DR_TXNS, NO_OF_L_CR_TXNS,NO_OF_CHQ_DR_TXNS, AMT_CHQ_DR, AMT_L_DR
#WEAK - OCCUPATION, BALANCE, BAL_CAP, AVG_AMT_PER_CHQ_TXN, FLG_HAS_CC, AMT_ATM_DR, NO_OF_NET_DR_TXNS, SCR, NO_OF_BR_CSH_WDL_DR_TXNS, AVG_AMT_PER_NET_TXN, AMT_NET_DR, AGE, AGE_BKT, AMT_BR_CSH_WDL_DR, ACC_TYPE, AVG_AMT_PER_CSH_WDL_TXN, GENDER
#VERY WEAK - FLG_HAS_ANY_CHGS

```

## Hypothesis statement
```
1. We dont have any strong variables as provided by iv
2. Among the average variables, we think the following
  a. Number of debit,credit transactions seems to have a relationship with people taking personal loan
  b. Balance or imputed balance cap are related to PL.
  c. People having credit card seem to be taking PL.
  d. Occupation also seems to be related to PL.
  e. People within a certain age bracket seems to be going for personal Loan
  
```

#Put together the visualization graphs
```{r}
colList = c("HOLDING_PERIOD", "NO_OF_L_DR_TXNS","TOT_NO_OF_L_TXNS", "NO_OF_ATM_DR_TXNS", "NO_OF_L_CR_TXNS","NO_OF_CHQ_DR_TXNS", "AMT_CHQ_DR", "AMT_L_DR","BALANCE", "BAL_CAP", "AVG_AMT_PER_CHQ_TXN", "FLG_HAS_CC", "AMT_ATM_DR", "NO_OF_NET_DR_TXNS", "SCR", "NO_OF_BR_CSH_WDL_DR_TXNS", "AVG_AMT_PER_NET_TXN", "AMT_NET_DR", "AGE","AMT_BR_CSH_WDL_DR", "AVG_AMT_PER_CSH_WDL_TXN")
source("C:/bigdata/Visualization-m.R")
source("C:/bigdata/Visualization.R")
output_folder = "C:/bigdata/VisualizationsAssignment-4/"
targetVarName = "TARGET"

#Converting the ACC_OP_DATE back to date
PL_XSELL$ACC_OP_DATE <- as.Date(PL_XSELL$ACC_OP_DATE)
for (i in 1 : length(colList)) {
  fn_biz_viz(df = PL_XSELL, target = targetVarName, var = colList[i])
}
fn_biz_viz_date(df = PL_XSELL, target = targetVarName,"ACC_OP_DATE")

```
## Sample the data into dev, val and hold
```{r}
#Sample the data into dev, val and hold on the basis of random 
myPlXsellData <- PL_XSELL
myPlXsellData.dev <- myPlXsellData[which(myPlXsellData$random <= 0.5),]
myPlXsellData.val <- myPlXsellData[which(myPlXsellData$random > 0.5 
                           & myPlXsellData$random <= 0.8 ),]
myPlXsellData.hold <- myPlXsellData[which(myPlXsellData$random > 0.8),]
nrow(myPlXsellData)
nrow(myPlXsellData.dev)
nrow(myPlXsellData.val)
nrow(myPlXsellData.hold)

sum(myPlXsellData$TARGET) / nrow(myPlXsellData)
sum(myPlXsellData.dev$TARGET)/ nrow(myPlXsellData.dev)
sum(myPlXsellData.val$TARGET)/ nrow(myPlXsellData.val)
sum(myPlXsellData.hold$TARGET)/ nrow(myPlXsellData.hold)
```
## Try running the model using all variables as identified by IV
```{r}

mylogit <- glm(
  TARGET ~ ACC_OP_DATE + HOLDING_PERIOD + NO_OF_L_DR_TXNS + TOT_NO_OF_L_TXNS + NO_OF_ATM_DR_TXNS + NO_OF_L_CR_TXNS + NO_OF_CHQ_DR_TXNS + AMT_CHQ_DR + 
AMT_L_DR + OCCUPATION + BALANCE  + AVG_AMT_PER_CHQ_TXN + 
FLG_HAS_CC + AMT_ATM_DR + NO_OF_NET_DR_TXNS + SCR + 
NO_OF_BR_CSH_WDL_DR_TXNS + AVG_AMT_PER_NET_TXN + AMT_NET_DR + AGE + AGE_BKT + AMT_BR_CSH_WDL_DR + ACC_TYPE + AVG_AMT_PER_CSH_WDL_TXN + GENDER +
FLG_HAS_ANY_CHGS ,  data = myPlXsellData.dev, family = "binomial"
)
summary(mylogit)

#After removing all insignificant variables, we are left with
#1 Holding Period
#2 TOT_NO_OF_L_TXNS
#3 AGE
#4 SCR
#5 OCCUPATION
#6 FLAG_HAS_CC
#7 GENDER

#Adding occupation imputed after taking into consideration
# that PROF, SENP and SAL
myPlXsellData.dev$OCCUPATION_Imputed =
  ifelse ( myPlXsellData.dev$OCCUPATION %in% c("SAL", "PROF","SENP"), "SAL-SENP-PROF",myPlXsellData.dev$OCCUPATION)

#Transform age
myPlXsellData.dev$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.dev$AGE_BKT %in% c("<25",">50"),"<25OR>50",                                   ifelse(myPlXsellData.dev$AGE_BKT %in% c("26-30","31-35"),"26-35",ifelse(myPlXsellData.dev$AGE_BKT %in% c("36-40","46-50"),"36-40OR46-50",myPlXsellData.dev$AGE_BKT)))

#Combine age even further after model output
myPlXsellData.dev$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.dev$AGE_BKT_IMPUTED %in% c("26-35","36-40OR46-50"),"26-40Or46-50",myPlXsellData.dev$AGE_BKT_IMPUTED)

#Combine age even further
myPlXsellData.dev$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.dev$AGE_BKT_IMPUTED %in% c("26-40Or46-50","<25OR>50"),"Non41-45",myPlXsellData.dev$AGE_BKT_IMPUTED)

age_bkt_imputed <- as.data.frame.matrix(table(myPlXsellData.dev$AGE_BKT_IMPUTED, myPlXsellData.dev$TARGET))
age_bkt_imputed$total <- (age_bkt_imputed$`0` + age_bkt_imputed$`1`)
age_bkt_imputed$rrate <- round(age_bkt_imputed$`1` * 100 / (age_bkt_imputed$`0` + age_bkt_imputed$`1`), 3)
age_bkt_imputed

#Initial Holding Period % split
hp <- as.data.frame.matrix(table(myPlXsellData.dev$HOLDING_PERIOD, myPlXsellData.dev$TARGET))
hp$total <- (hp$`0` + hp$`1`)
hp$rrate <- round(hp$`1` * 100 / (hp$`0` + hp$`1`), 3)
hp

#Impute holding period
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(17,20,22,23,25,26,28,30), "6-9",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(24,27,29,31),"3-4",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(16,19),"10-11",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(5,7,9,11,14,18,21),"12-13",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(4,6,8,12,13,15),"14-15",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(3),"16",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(10),"18",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(2),"21",ifelse(myPlXsellData.dev$HOLDING_PERIOD %in% c(1),"25","NA")))))))))


#Check for correctness whether any unwanted NA is inadvertently introduced
unique(myPlXsellData.dev$HP_IMPUTED)
#Impute holding period further after 1 model run
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("12-13","14-15"),"12-15",myPlXsellData.dev$HP_IMPUTED)
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("16","18"),"16OR18",myPlXsellData.dev$HP_IMPUTED)
#Impute holding period further after 2 model run
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("12-15","16OR18"),"12-18",myPlXsellData.dev$HP_IMPUTED)
#Impute holding period further after 3 model run
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("12-18","10-11"),"10-18",myPlXsellData.dev$HP_IMPUTED)
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("3-4","6-9"),"3-9",myPlXsellData.dev$HP_IMPUTED)
#Imput further after 4 model run
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("21","25"),"21-25",myPlXsellData.dev$HP_IMPUTED)


# After all the imputations, below is the split category
hp_i <- as.data.frame.matrix(table(myPlXsellData.dev$HP_IMPUTED, myPlXsellData.dev$TARGET))
hp_i$total <- (hp_i$`0` + hp_i$`1`)
hp_i$rrate <- round(hp_i$`1` * 100 / (hp_i$`0` + hp_i$`1`), 3)
hp_i

unique(myPlXsellData.dev$HP_IMPUTED)

# run model after all imputations and corrections
mylogit <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BALANCE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.dev, family = "binomial"
)
summary(mylogit)


```
## Do model validation for Ks, goodnessof fit and concordance
```{r}
#Use predict to get the probability for the ones present in model
#for their hit/miss
View(myPlXsellData.dev)
myPlXsellData.dev$prob <- predict(mylogit, myPlXsellData.dev, type="response")
myPlXsellData.dev$deciles <- decile(myPlXsellData.dev$prob)
#class(myPlXsellData.dev)

#calculate rank ordering
tmp_PlXsellDT = data.table(myPlXsellData.dev)
rankPlXsell <- tmp_PlXsellDT[, list(    
  cnt = length(TARGET), 
  cnt_resp = sum(TARGET), 
  cnt_non_resp = sum(TARGET == 0)) , 
  by=deciles][order(-deciles)]
rankPlXsell$rrate <- round (rankPlXsell$cnt_resp / rankPlXsell$cnt,3);
rankPlXsell$cum_resp <- cumsum(rankPlXsell$cnt_resp)
rankPlXsell$cum_non_resp <- cumsum(rankPlXsell$cnt_non_resp)
rankPlXsell$cum_rel_resp <- round(rankPlXsell$cum_resp / sum(rankPlXsell$cnt_resp),3);
rankPlXsell$cum_rel_non_resp <- round(rankPlXsell$cum_non_resp / sum(rankPlXsell$cnt_non_resp),3);
rankPlXsell$ks <- percent(abs(rankPlXsell$cum_rel_resp - rankPlXsell$cum_rel_non_resp));
rankPlXsell$rrate <- percent(rankPlXsell$rrate)
rankPlXsell$cum_rel_resp <- percent(rankPlXsell$cum_rel_resp)
rankPlXsell$cum_rel_non_resp <- percent(rankPlXsell$cum_rel_non_resp)

View(rankPlXsell)

############ Goodness of Fit: ##############
# A function to do the Hosmer-Lemeshow test in R.
# R Function is due to Peter D. M. Macdonald, McMaster University.
head(myPlXsellData.dev)
ttt <- data.table(myPlXsellData.dev)
sqldf('select deciles, count(1) as cnt_cust,
      sum(TARGET) as cnt_resp,
      sum(prob) as est_rep
from ttt
group by deciles'
)


hosmerlem <-
  function (y, yhat, g = 10) 
  {
    cutyhat <- cut(yhat, breaks = quantile(yhat, probs = seq(0, 
                                                             1, 1/g)), include.lowest = T)
    obs <- xtabs(cbind(1 - y, y) ~ cutyhat)
    expect <- xtabs(cbind(1 - yhat, yhat) ~ cutyhat)
    chisq <- sum((obs - expect)^2/expect)
    P <- 1 - pchisq(chisq, g - 2)
    c("X^2" = chisq, Df = g - 2, "P(>Chi)" = P)
  }

hl_gofPlXsell = hosmerlem(myPlXsellData.dev$TARGET, myPlXsellData.dev$prob)
hl_gofPlXsell

#***FUNCTION TO CALCULATE CONCORDANCE AND DISCORDANCE***#
concordance=function(y, yhat)
{
  Con_Dis_Data = cbind(y, yhat) 
  ones = Con_Dis_Data[Con_Dis_Data[,1] == 1,]
  zeros = Con_Dis_Data[Con_Dis_Data[,1] == 0,]
  conc=matrix(0, dim(zeros)[1], dim(ones)[1])
  disc=matrix(0, dim(zeros)[1], dim(ones)[1])
  ties=matrix(0, dim(zeros)[1], dim(ones)[1])
  for (j in 1:dim(zeros)[1])
  {
    for (i in 1:dim(ones)[1])
    {
      if (ones[i,2]>zeros[j,2])
      {conc[j,i]=1}
      else if (ones[i,2]<zeros[j,2])
      {disc[j,i]=1}
      else if (ones[i,2]==zeros[j,2])
      {ties[j,i]=1}
    }
  }
  Pairs=dim(zeros)[1]*dim(ones)[1]
  PercentConcordance=(sum(conc)/Pairs)*100
  PercentDiscordance=(sum(disc)/Pairs)*100
  PercentTied=(sum(ties)/Pairs)*100
  return(list("Percent Concordance"=PercentConcordance,"Percent Discordance"=PercentDiscordance,"Percent Tied"=PercentTied,"Pairs"=Pairs))
}

concordance_output = concordance(myPlXsellData.dev$TARGET, myPlXsellData.dev$prob)
concordance_output

# Goodness of fit has problems, hence need to re-look at other significant variables 

# Balance has got some cracks, fixing those by considering Balance bucket followed by BAL_WOE
myPlXsellData.dev$BAL_BKT <- ifelse(myPlXsellData.dev$BALANCE <= 9200, "<=9200",
                      ifelse(myPlXsellData.dev$BALANCE <= 66000, "9.2k - 66k",
                      ifelse(myPlXsellData.dev$BALANCE <= 116000,"66k - 116k",
                      ifelse(myPlXsellData.dev$BALANCE <= 190000,"116k - 190k",
                      ifelse(myPlXsellData.dev$BALANCE <= 660000,"190k - 660k",
                      ifelse(myPlXsellData.dev$BALANCE <= 2300000,"660k-2300k",">2300k"))))))

# Take the table output and then convert the same into a WOE
table(myPlXsellData.dev$BAL_BKT,myPlXsellData.dev$TARGET)                      

#Take the WOE output from excel as below
myPlXsellData.dev$BAL_WOE <- ifelse(myPlXsellData.dev$BALANCE <= 9200, -53.64,
                      ifelse(myPlXsellData.dev$BALANCE <= 66000, -26.74,
                      ifelse(myPlXsellData.dev$BALANCE <= 116000,-8.76,
                      ifelse(myPlXsellData.dev$BALANCE <= 190000,11.3,
                      ifelse(myPlXsellData.dev$BALANCE <= 660000,3.83,
                      ifelse(myPlXsellData.dev$BALANCE <= 2300000,34.37,49.13))))))

#re-run model after changing from BALANCE to BAL_WOE
mylogit <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BAL_WOE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.dev, family = "binomial"
)
summary(mylogit)

#re-run goodness of fit again
#Finally got a goodness of fit which is
#     X^2          Df      P(>Chi) 
# 18.76871653  8.00000000  0.01614671 

```

## Run the model against the validation sample and compare model performance
```{r}
myPlXsellData.val$OCCUPATION_Imputed =
  ifelse ( myPlXsellData.val$OCCUPATION %in% c("SAL", "PROF","SENP"), "SAL-SENP-PROF",myPlXsellData.val$OCCUPATION)

#Transform age
myPlXsellData.val$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.val$AGE_BKT %in% c("<25",">50"),"<25OR>50",                                   ifelse(myPlXsellData.val$AGE_BKT %in% c("26-30","31-35"),"26-35",ifelse(myPlXsellData.val$AGE_BKT %in% c("36-40","46-50"),"36-40OR46-50",myPlXsellData.val$AGE_BKT)))

#Combine age even further after model output
myPlXsellData.val$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.val$AGE_BKT_IMPUTED %in% c("26-35","36-40OR46-50"),"26-40Or46-50",myPlXsellData.val$AGE_BKT_IMPUTED)

#Combine age even further
myPlXsellData.val$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.val$AGE_BKT_IMPUTED %in% c("26-40Or46-50","<25OR>50"),"Non41-45",myPlXsellData.val$AGE_BKT_IMPUTED)

#Impute holding period
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(17,20,22,23,25,26,28,30), "6-9",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(24,27,29,31),"3-4",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(16,19),"10-11",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(5,7,9,11,14,18,21),"12-13",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(4,6,8,12,13,15),"14-15",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(3),"16",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(10),"18",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(2),"21",ifelse(myPlXsellData.val$HOLDING_PERIOD %in% c(1),"25","NA")))))))))


#Impute holding period further after 1 model run
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("12-13","14-15"),"12-15",myPlXsellData.val$HP_IMPUTED)
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("16","18"),"16OR18",myPlXsellData.val$HP_IMPUTED)
#Impute holding period further after 2 model run
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("12-15","16OR18"),"12-18",myPlXsellData.val$HP_IMPUTED)
#Impute holding period further after 3 model run
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("12-18","10-11"),"10-18",myPlXsellData.val$HP_IMPUTED)
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("3-4","6-9"),"3-9",myPlXsellData.val$HP_IMPUTED)
#Imput further after 4 model run
myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("21","25"),"21-25",myPlXsellData.val$HP_IMPUTED)


#Balance transformation
myPlXsellData.val$BAL_BKT <- ifelse(myPlXsellData.val$BALANCE <= 9200, "<=9200",
                      ifelse(myPlXsellData.val$BALANCE <= 66000, "9.2k - 66k",
                      ifelse(myPlXsellData.val$BALANCE <= 116000,"66k - 116k",
                      ifelse(myPlXsellData.val$BALANCE <= 190000,"116k - 190k",
                      ifelse(myPlXsellData.val$BALANCE <= 660000,"190k - 660k",
                      ifelse(myPlXsellData.val$BALANCE <= 2300000,"660k-2300k",">2300k"))))))

#Take the WOE output from excel as below
myPlXsellData.val$BAL_WOE <- ifelse(myPlXsellData.val$BALANCE <= 9200, -53.64,
                      ifelse(myPlXsellData.val$BALANCE <= 66000, -26.74,
                      ifelse(myPlXsellData.val$BALANCE <= 116000,-8.76,
                      ifelse(myPlXsellData.val$BALANCE <= 190000,11.3,
                      ifelse(myPlXsellData.val$BALANCE <= 660000,3.83,
                      ifelse(myPlXsellData.val$BALANCE <= 2300000,34.37,49.13))))))


# run model after all imputations and corrections
mylogit.val <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BAL_WOE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.val, family = "binomial"
)
summary(mylogit.val)


```
## Compare dev and validations
```{r}
# The dev and validation sample shows a ration < 0.5 for transformed significant variable HP_IMPUTED3-9
# This then has to be transformed further to bring stability back
# Combine 3-9 holding period with its nearest ration which is 10-18
myPlXsellData.dev$HP_IMPUTED <- ifelse(myPlXsellData.dev$HP_IMPUTED %in% c("3-9","10-18"),"3-18",myPlXsellData.dev$HP_IMPUTED)

#Run both data and validation models and compare
mylogit <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BAL_WOE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.dev, family = "binomial"
)
summary(mylogit)

myPlXsellData.val$HP_IMPUTED <- ifelse(myPlXsellData.val$HP_IMPUTED %in% c("3-9","10-18"),"3-18",myPlXsellData.val$HP_IMPUTED)


mylogit.val <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BAL_WOE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.val, family = "binomial"
)
summary(mylogit.val)

```

## Final ratio comparison result
```
Val						Ratio = Val/Dev		Dev					
	Estimate	Std. Error	z value	Pr(>|z|)					Estimate	Std. Error	z value	Pr(>|z|)	
(Intercept)	-2.1546215	0.1767695	-12.189	< 2e-16	***	1.095977215		(Intercept)	-1.9659364	0.1315412	-14.945	< 2e-16	***
HP_IMPUTED3-18	-0.7865961	0.1238845	-6.349	2.16E-10	***	0.887250599		HP_IMPUTED3-18	-0.8865546	0.0924354	-9.591	< 2e-16	***
TOT_NO_OF_L_TXNS	0.0168207	0.0018841	8.927	< 2e-16	***	0.976097629		TOT_NO_OF_L_TXNS	0.0172326	0.001425	12.093	< 2e-16	***
AGE_BKT_IMPUTEDNon41-45	-0.4422792	0.1047056	-4.224	2.40E-05	***	1.361172356		AGE_BKT_IMPUTEDNon41-45	-0.3249252	0.0794923	-4.088	4.36E-05	***
OCCUPATION_ImputedSELF-EMP	0.8024122	0.0931204	8.617	< 2e-16	***	1.199354176		OCCUPATION_ImputedSELF-EMP	0.6690369	0.0720918	9.28	< 2e-16	***
BAL_WOE	-0.0079606	0.0015997	-4.976	6.48E-07	***	1.071485295		BAL_WOE	-0.0074295	0.0012243	-6.069	1.29E-09	***
FLG_HAS_CC	0.6489127	0.0840603	7.72	1.17E-14	***	1.058828357		FLG_HAS_CC	0.6128592	0.0637013	9.621	< 2e-16	***
SCR	0.0009863	0.0001595	6.185	6.20E-10	***	1.18204698		SCR	0.0008344	0.0001212	6.886	5.74E-12	***

```
## Running this finally on hold data
```{r}
myPlXsellData.hold$OCCUPATION_Imputed =
  ifelse ( myPlXsellData.hold$OCCUPATION %in% c("SAL", "PROF","SENP"), "SAL-SENP-PROF",myPlXsellData.hold$OCCUPATION)

#Transform age
myPlXsellData.hold$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.hold$AGE_BKT %in% c("<25",">50"),"<25OR>50",                                   ifelse(myPlXsellData.hold$AGE_BKT %in% c("26-30","31-35"),"26-35",ifelse(myPlXsellData.hold$AGE_BKT %in% c("36-40","46-50"),"36-40OR46-50",myPlXsellData.hold$AGE_BKT)))

#Combine age even further after model output
myPlXsellData.hold$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.hold$AGE_BKT_IMPUTED %in% c("26-35","36-40OR46-50"),"26-40Or46-50",myPlXsellData.hold$AGE_BKT_IMPUTED)

#Combine age even further
myPlXsellData.hold$AGE_BKT_IMPUTED <- ifelse(myPlXsellData.hold$AGE_BKT_IMPUTED %in% c("26-40Or46-50","<25OR>50"),"Non41-45",myPlXsellData.hold$AGE_BKT_IMPUTED)

#Impute holding period
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(17,20,22,23,25,26,28,30), "6-9",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(24,27,29,31),"3-4",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(16,19),"10-11",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(5,7,9,11,14,18,21),"12-13",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(4,6,8,12,13,15),"14-15",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(3),"16",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(10),"18",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(2),"21",ifelse(myPlXsellData.hold$HOLDING_PERIOD %in% c(1),"25","NA")))))))))


#Impute holding period further after 1 model run
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("12-13","14-15"),"12-15",myPlXsellData.hold$HP_IMPUTED)
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("16","18"),"16OR18",myPlXsellData.hold$HP_IMPUTED)
#Impute holding period further after 2 model run
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("12-15","16OR18"),"12-18",myPlXsellData.hold$HP_IMPUTED)
#Impute holding period further after 3 model run
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("12-18","10-11"),"10-18",myPlXsellData.hold$HP_IMPUTED)
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("3-4","6-9"),"3-9",myPlXsellData.hold$HP_IMPUTED)
#Imput further after 4 model run
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("21","25"),"21-25",myPlXsellData.hold$HP_IMPUTED)
myPlXsellData.hold$HP_IMPUTED <- ifelse(myPlXsellData.hold$HP_IMPUTED %in% c("3-9","10-18"),"3-18",myPlXsellData.hold$HP_IMPUTED)



#Balance transformation
myPlXsellData.hold$BAL_BKT <- ifelse(myPlXsellData.hold$BALANCE <= 9200, "<=9200",
                      ifelse(myPlXsellData.hold$BALANCE <= 66000, "9.2k - 66k",
                      ifelse(myPlXsellData.hold$BALANCE <= 116000,"66k - 116k",
                      ifelse(myPlXsellData.hold$BALANCE <= 190000,"116k - 190k",
                      ifelse(myPlXsellData.hold$BALANCE <= 660000,"190k - 660k",
                      ifelse(myPlXsellData.hold$BALANCE <= 2300000,"660k-2300k",">2300k"))))))

#Take the WOE output from excel as below
myPlXsellData.hold$BAL_WOE <- ifelse(myPlXsellData.hold$BALANCE <= 9200, -53.64,
                      ifelse(myPlXsellData.hold$BALANCE <= 66000, -26.74,
                      ifelse(myPlXsellData.hold$BALANCE <= 116000,-8.76,
                      ifelse(myPlXsellData.hold$BALANCE <= 190000,11.3,
                      ifelse(myPlXsellData.hold$BALANCE <= 660000,3.83,
                      ifelse(myPlXsellData.hold$BALANCE <= 2300000,34.37,49.13))))))


# run model after all imputations and corrections
mylogit.hold <- glm(
  TARGET ~  
    HP_IMPUTED +
    TOT_NO_OF_L_TXNS + 
    AGE_BKT_IMPUTED +
    OCCUPATION_Imputed + BAL_WOE + FLG_HAS_CC + SCR
    ,  data = myPlXsellData.hold, family = "binomial"
)
summary(mylogit.hold)

# Rank Order
myPlXsellData.hold$prob <- predict(mylogit, myPlXsellData.hold, type="response")
myPlXsellData.hold$deciles <- decile(myPlXsellData.hold$prob)

tmp_PlXsellDT = data.table(myPlXsellData.hold)
rank <- tmp_PlXsellDT[, list(    
  cnt = length(TARGET), 
  cnt_resp = sum(TARGET), 
  cnt_non_resp = sum(TARGET == 0)) , 
  by=deciles][order(-deciles)]
rank$rrate <- round (rank$cnt_resp / rank$cnt,3);
rank$cum_resp <- cumsum(rank$cnt_resp)
rank$cum_non_resp <- cumsum(rank$cnt_non_resp)
rank$cum_rel_resp <- round(rank$cum_resp / sum(rank$cnt_resp),3);
rank$cum_rel_non_resp <- round(rank$cum_non_resp / sum(rank$cnt_non_resp),3);
rank$ks <- percent(abs(rank$cum_rel_resp - rank$cum_rel_non_resp));
rank$rrate <- percent(rank$rrate)
rank$cum_rel_resp <- percent(rank$cum_rel_resp)
rank$cum_rel_non_resp <- percent(rank$cum_rel_non_resp)

View(rank)



```
